---
title: "Apply"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
```


#### Suppose we have a function called `toFahrenheit`, which accepts a temperature in Celsius, `temperature`, and returns that temperature in Fahrenheit.
```{r}
toFahrenheit <- function(temperature) {
  fahrenheit <- temperature * 1.8 + 32
  return(fahrenheit)
}
```

#### A list of temperatures in Celsius called `celsius`
```{r}
celsius <- c(0, -2, 0, 5.2, 5.4)
```

#### Create a new list, `fahrenheit`, containing the values in `celsius` converted to Fahrenheit.
#### Solution: Valid...But noisy.
```{r}
fahrenheit <- numeric()
for (i in 1:length(celsius)) {
  temperature_fahrenheit <- toFahrenheit(celsius[i])
  fahrenheit[i] <- temperature_fahrenheit
}
```
#### Results
```{r}
fahrenheit
```

#### `sapply` provides a succinct alternative.
```{r}
fahrenheit2 <- sapply(celsius, toFahrenheit)
fahrenheit2
```

#### Use `lapply` when you know you need a list, and _not_ a vector.
```{r}
fahrenheit3 <- lapply(celsius, toFahrenheit)
fahrenheit3
```

